A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Fixed centring of example graphs G and H

\newcommand{\exampleG} {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=5] {
                    1,2,3,4,5;
            1--4; 1--5; 2--3; 2--5; 3--5;
        };
    }
    \end{minipage}
}
\newcommand{\exampleH} {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=6, phase=60] {
                    a,b,c,d,e,f;
            a--b; a--c; a--e; b--d; b--f; c--d; c--e; c--f; d--f; e--f;
        };
    }
    \end{minipage}
}

@@

\begin{figure}[t]
\centering
    \exampleG
    \exampleH
\caption{Example graphs $G$ and $H$.}
\label{fig:alg1}
\end{figure}

>>>>

\newcommand{\exampleG} {
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=5] {
                    1,2,3,4,5;
            1--4; 1--5; 2--3; 2--5; 3--5;
        };
    }
}
\newcommand{\exampleH} {
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=6, phase=60] {
                    a,b,c,d,e,f;
            a--b; a--c; a--e; b--d; b--f; c--d; c--e; c--f; d--f; e--f;
        };
    }
}

@@

\begin{figure}[t]
\centering
    \exampleG
    \qquad
    \exampleH
\caption{Example graphs $G$ and $H$.}
\label{fig:alg1}
\end{figure}
